\documentclass[a4paper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,bindingoffset=0in, left=1.0in,right=1.0in,top=1.2in,bottom=1.2in]{geometry}
\usepackage{multicol}
\usepackage{graphicx} % Required for inserting images
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{amsmath}


\usepackage{titlesec}
\titleformat{\chapter}{\bfseries\LARGE}{\thechapter~}{1em}{}
\titlespacing{\chapter}{0in}{0in}{0.25in}

\usepackage[hyphens]{url}
\usepackage{hyperref}
\urlstyle{same} 
\hypersetup{colorlinks=true, linkcolor=black, filecolor=black, urlcolor=black, citecolor=cyan}

\usepackage[british]{babel}
\usepackage{setspace}
\setstretch{1.5}
\usepackage{parskip}
\setlength{\parindent}{0pt}

\newcommand{\abbrlabel}[1]{\makebox[1in][l]{\textbf{#1}\ }}
\newenvironment{Abbreviations}{\begin{list}{}{\renewcommand{\makelabel}{\abbrlabel}}}{\end{list}}

\makeatletter
\renewcommand\@biblabel[1]{}
\renewenvironment{thebibliography}[1]
     {\section*{\refname}%
      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
      \list{}%
           {\leftmargin0pt
           \advance\leftmargin2em
           \setlength\itemindent{-2em}
            \@openbib@code
            \usecounter{enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother

\usepackage{cite}
\renewcommand\citeleft{}
\renewcommand\citeright{}

\pagestyle{plain}
\fancyhead[R]{Meier, Merki, and Thimóteo}
\fancyhead[C]{}
\fancyhead[L]{\rightmark}
\fancyfoot[L]{}
\fancyfoot[C]{\thepage}
\fancyfoot[R]{}

\title{Currency risks for Swiss residents}
%\author{}
\date{November 2023}

\begin{document}

\maketitle

\newpage
\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{Roman}
\tableofcontents

\newpage
\pagestyle{plain}
\listoffigures
\addcontentsline{toc}{section}{List of Figures}

\newpage
\begingroup
\vspace{4ex}
\let\clearpage\relax
\listoftables
\endgroup
\addcontentsline{toc}{section}{List of Tables}

\newpage
\pagestyle{plain}
\section*{Abbreviations}
\addcontentsline{toc}{section}{Abbreviations}
\begin{Abbreviations}
\item[CBOE] Chicago Board Options Exchange 
\item[CHF] Swiss franc
\item[EUR] Euro
\item[FRED] Federal Reserve Economic Data 
\item[OECD] Organisation for Economic Co-operation and Development
\item[SNB] Swiss National Bank
\item[USD] US dollar
\item[VIX] CBOE Volatility Index
\end{Abbreviations}


\newpage
\pagestyle{fancy}
\setcounter{page}{1}
\pagenumbering{arabic}

\section{Introduction}\label{Introduction}
The Covid crisis in 2019 confirmed once more the safe haven currency status of the Swiss franc (CHF) based on the characteristic proposed by \cite{Habib and Stracca 2012}. While a safe haven currency status might be beneficial from a value storage perspective, it certainly presents challenges regarding other perspectives. The aim of this paper is to determine the riskiest currency to hold for a Swiss investor. It is based on the works of \cite{Grisse and Nitschka 2015}, \cite{Verdelhan 2010}, \cite{Backus and Foresi and Telmer 2001}, and \cite{Lustig and Roussanov and Verdelhan 2011}. The analysis consists of 9 CHF exchange rate pairs starting from April 2002 to November 2023 based on the framework of \cite{Grisse and Nitschka 2015} with one CHF-specific (\emph{AFX}) and one global risk factor (\emph{VIX}).\par

%mention effect

%\textcolor{red}{reproduce the findings of \cite{Grisse and Nitschka 2015} and provide an actualised version of their work.}

Our results highlight...\par

The paper is structured as follows. Section \ref{Theoretical background} briefly elaborates on the theoretical background. Section \ref{Data} discloses the data sources. Section \ref{Analysis} contains the analysis with the results. Section \ref{Conclusion} provides a conclusion.\par 

  
\section{Theoretical background}\label{Theoretical background}
\subsection{Uncovered Interest Rate Parity}\label{Uncovered Interest Rate Parity}
\begin{equation}\label{1}
\mathcal{F}_{t,k}=S_{t}\frac{(1+i_{t,k})^k}{(1+i_{t,k}^*)^k}
\end{equation}

\section{Data}\label{Data}
The time span (April 2002 to November 2023) of the data is limited by the data series for Japan. This renders the bridge solution for the euro (EUR), as presented in \cite{Grisse and Nitschka 2015}, redundant. The exchange rates were retrieved as end of the month US dollar (USD) cross-rates from the Federal Reserve Economic Data (FRED) and converted into end of the month CHF exchange rates. The short-term interest rates were retrieved monthly as end of the month from the Organisation for Economic Co-operation and Development (OECD) database. The Chicago Board Options Exchange (CBOE) Volatility Index (VIX) was also retrieved monthly as end of the month from FRED.\par
 


\section{Analysis}\label{Analysis}
slides 21/90
\subsection{Model}\label{Model}
\begin{equation}\label{2}
\Delta s_{t+1}^k=\alpha^k+\beta_{0}^k(f_{t}^k-s_{t}^k)+\beta_{1}^k AFX_{t+1}+\beta_{2}^k\Delta VIX_{t+1}+\epsilon_{t+1}^k
\end{equation}
\section{Conclusion}\label{Conclusion}


\newpage
\pagestyle{plain}
\renewcommand{\refname}{Bibliography}
\addcontentsline{toc}{section}{Bibliography}
\begin{thebibliography}{99}

\bibitem[Backus, Foresi, and Telmer (2001)]{Backus and Foresi and Telmer 2001}\href{https://doi.org/10.1111/0022-1082.00325}{Backus, David K., Silverio Foresi, and Chris I. Telmer, 2001, Affine Term Structure Models and the Forward Premium Anomaly, pp. 279--304 in \textit{Journal of Finance}, Vol. 56, No. 1, February.}

\bibitem[Grisse and Nitschka (2015)]{Grisse and Nitschka 2015}\href{https://doi.org/10.1016/j.jempfin.2015.03.006}{Grisse, Christian, and Thomas Nitschka, 2013, On financial risk and the safe haven characteristics of Swiss franc exchange rates, pp. 153--164 in \textit{Journal of Empirical Finance}, Vol. 32, June.}

\bibitem[Habib and Stracca (2012)]{Habib and Stracca 2012}\href{https://doi.org/10.1016/j.jinteco.2011.12.005}{Habib, Maurizio M., and Livio Stracca, 2012, Getting beyond carry trade: What makes a safe haven currency?, pp. 50--64 in \textit{Journal of International Economics}, Vol. 87, No. 1, May.}

\bibitem[Lustig, Roussanov, and Verdelhan (2011)]{Lustig and Roussanov and Verdelhan 2011}\href{https://www.jstor.org/stable/41301998}{Lustig, Hanno, Nikolai Roussanov, and Adrien Verdelhan, 2011, Common Risk Factors in Currency Markets, pp. 3731--3777 in \textit{Review of Financial Studies}, Vol. 24, No. 11, November.}

\bibitem[Verdelhan (2010)]{Verdelhan 2010}\href{https://doi.org/10.1111/j.1540-6261.2009.01525.x}{Verdelhan, Adrien, 2010, A Habit-Based Explanation of the Exchange Rate Risk Premium, pp. 123--146 in \textit{Journal of Finance}, Vol. 65, No. 1, February.}






%\bibitem[Akerlof (1970)]{Akerlof 1970}\href{https://doi.org/10.2307/1879431}{Akerlof, George Arthur, 1970, The Market for "Lemons": Quality Uncertainty and the Market Mechanism, pp. 488--500 in \textit{The Quarterly Journal of Economics}, Vol. 83, No. 3, August.}





\end{thebibliography}

\appendix
\newpage
\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{Roman}
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}

\end{document}



